---
title: "EcoMan"
output:
  html_document: 
    highlight: kate
    theme: united
    toc: yes
date: "April 20, 2019"
---

```{r setup, include=FALSE, eval=TRUE}
library(ggplot2)
```

## Creating Economic Model for Oil and Gas Projects _**EcoMan**_
### Writing The Economic Functions

```{r func, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
### Writing the Economic Functions to calculate DCF, NPV, IRR and PBP, DPBP

dcf <- function(x, r, t0=FALSE){
  # calculates discounted cash flows (DCF) given cash flow and discount rate
  #
  # x - cash flows vector
  # r - vector or discount rates, in decimals. Single values will be recycled
  # t0 - cash flow starts in year 0, default is FALSE, i.e. discount rate in first period is zero.
  if(length(r)==1){
    r <- rep(r, length(x))
    if(t0==TRUE){r[1]<-0}
    }
  x/cumprod(1+r)
 }

npv <- function(x, r, t0=FALSE){
  # calculates net present value (NPV) given cash flow and discount rate
  #
  # x - cash flows vector
  # r - discount rate, in decimals
  # t0 - cash flow starts in year 0, default is FALSE
  sum(dcf(x, r, t0))
 }

pbp <- function(x, ...){
  # calculates payback period (PBP)
  #
  # x - cash flows vector
  # ... - ignored
  i <- match(1, sign(cumsum(x)))
  i-2+(-cumsum(x)[i-1]/x[i])
 }

dpbp <- function(x, r, t0=FALSE){
  # calculates discounted payback period (DPBP) given cash flow and discount rate
  #
  # x - cash flows vector
  # r - discount rate, in decimals
  # t0 - cash flow starts in year 0, default is FALSE
  pbp(dcf(x, r, t0))
 }

irr <- function(x, t0=FALSE, ...){
  # calculates internal rate of return (IRR) given cash flow 
  #
  # x - cash flows vector
  # t0 - cash flow starts in year 0, default is FALSE
tryCatch(uniroot(f=function(i){sum(dcf(x, i, t0))}, 
                 interval=c(0,1))$root,
         error=function(e) return(NA)
        )
  }

```
## The Input data
We have two different projects to be evaluated based on the folowing economic parameters:  
- Net Present Value _**NPV**_  
- Internal Rate of Return _**IRR**_  
- Pay back Period _**PBP**_  
- Discounted Pay back Period _**DPBP**_  
- Discounted Cash Flow _**DCF**_  

```{r}
### the Two Project that needed to be evaluated
# To evaluate the two projects they should have the same project time
#together to evaluate them together or you should evaluate them separately
  Time.Evaluation <-c(1:6)
  Project1 <- c(-1000, 1250, 10, 10, 20, 20)
  Project2 <- c(-1000, -10, 0, 10, 20, 2000)
  Projects.data <- data.frame(Time.Evaluation, Project1 , Project2)
  knitr::kable(Projects.data)
```

## The Method of Evaluations
### 1. Calculating the Discounted Cash Flow _**DCF**_  
To understand the time value of Money for the two projects.
```{r}
### Calculating the Discounted Cash Flow "DCF"
### the interest rate given is 0.06 "6%"

CDF.P1 <- dcf(Project1, r= 0.06, t0=TRUE)
cdfProject1<- data.frame(Time.Evaluation, Project1,CDF.P1)
knitr::kable(cdfProject1)

CDF.P2 <- dcf(Project2, r= 0.06, t0=TRUE)
cdfProject2<- data.frame(Time.Evaluation, Project2,CDF.P2)
knitr::kable(cdfProject2)

```

### 2. Claculating Net Present Value _**NPV**_    
To understand the Whole project monetry value in the present day.
```{r}
### NPV Calculations
npv.p1 <- npv(Project1, r=0.06, t0 = TRUE)
npv.p2 <- npv(Project2, r=0.06, t0 = TRUE)
npv.all <- data.frame(npv.p1,npv.p2)
knitr::kable(npv.all)
#ggplot(npv.all)+geom_col(aes(x= as.factor(colnames(npv.all)), y= npv.all))
plot(npv.all, type = "p")
```

### 3. Calculating the Payback Period _**PBP**_  
```{r}
### PayBack Period Calculations
pbp.p1<- pbp(Project1)
pbp.p2<- pbp(Project2)
pbp.all <- data.frame(pbp.p1,pbp.p2)
knitr::kable(pbp.all)
dpbp.p1 <- dpbp(Project1, r= 0.06, t0=TRUE)
dpbp.p2 <- dpbp(Project2, r= 0.06, t0=TRUE)
dpbp.all <- data.frame(dpbp.p1,dpbp.p2)
knitr::kable(dpbp.all)

```


### 4. Calculating the Internal Rate Of Return _**IRR**_

```{r}
### IRR Calculations 
IRR.P1 <- irr(Project1)
IRR.P2 <- irr(Project2)
IRR.all <- data.frame(IRR.P1,IRR.P2)
knitr::kable(IRR.all)
```

