---
title: "Production Profile"
output:
  html_document: 
    highlight: kate
    theme: united
    toc: yes
date: "March 30, 2017"
---
############################################


###  **Production profile**

to create production profile you need initial production (Pi), duration(Time), and the decline rate(DR) 

## the inputs to the model
```{r production}
 
 library(ggplot2)

Pi <- 2000
Duration = c(0:10)
DR <- 0.2
#df <- data.frame(Duration,Pi)
df <- NULL

for (i in Duration) {
  
  Pi = Pi- (Pi*DR)
 # print(paste(round(Pi,0),i+1))

df <- rbind(df,data.frame(i, round(Pi,0)))
#df <- rbind(df,i, round(Pi,0))

}

#df
names(df)[1] <- "Time"
names(df)[2] <- "Production"

```

## the expected production per day yearly 
```{r output, echo=TRUE, message=FALSE, warning=FALSE}
knitr::kable(df)

```

## a graph shows the production forecast for the field life time
```{r}
p<- ggplot(df, aes(Time,Production))+geom_point()+geom_line(colour = "blue")
plotly::ggplotly(p)
```

## the Cumulative production during the 'Duration' 
```{r}
print(paste('the total production is' , sum(df$Production)*365))
```

############################################

Please dont hesitate to contact me over a_moslim@live.com to share your comments. 