---
title: "My Own Website, Bitecheesssss"
author: "Amrmoslim"
date: "March 30, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My Motive objective 


A versatile and highly skilled Geophysicist with 9+ years industry experience, and wide ranging expertise from interpretation in exploration and resource development to 3D depth imaging technology development and application using a wide range of geosciences software. Experienced in seismic interpretation, prospect generation; computer mapping and 3D visualization. Adept at working and communicating across disciplines and management levels. Have been both a popular and highly effective contributor to each of the teams worked with.

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
