---
title: "Amr Mahmoud Abdelfattah"
date: "June 27, 2021"
output:
  html_document: 
    highlight: kate
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

#### **PERSONAL PROFILE**


A versatile and highly skilled Geophysicist with 12 years industry experience, and wide ranging expertise from interpretation in exploration and resource development to 3D depth imaging technology development and application using a wide range of geosciences software. Experienced in seismic interpretation, prospect generation; computer mapping and 3D visualization. Adept at working and communicating across disciplines and management levels. Have been both a popular and highly effective contributor to each of the teams worked with.

#### **EDUCATION & TRAINING COURSES**

- B.Sc in Geophysics, Faculty of Science, Cairo University (2006)
-	Project Management MiniMBA, accredited from PMI (Ongoing)
- Structural Restoration Modeling & Fault Prediction 
-	Velocity analysis course, Schlumberger
-	Advanced Seismic Interpretation.
-	Application of Structural Geology in Seismic Data Interpretation.
-	Risk Identification and Assessment.
-	Prospective and Contingent Resources within PRMS. (Gaffney,Cline& Associates)
-	Several QHSE internal awareness sessions.
-	Economics 101 				*Stanford online university*
-	Reservoir Geomechanics 			*Stanford online university*

#### **EXTRACURRICULAR ACTIVITIES**

-	Working as freelance instructor for Seismic Interpretation Methods, Fault Seal Analysis and Advanced Seismic Interpretation courses.
- Creating and developing Android application for Fault Seal Analysis Quick look.

#### **PROGRAMS & COMPUTER SKILLS**

-	Petrel (Slb)
-	Kingdom (SMT)
-	GeoFrame ( Charisma software- Imain and CPS-3)
-	Lithotect (GLS)  (Restoration)
- Hampson Russell.  
- Office programs (Word, Excel, PowerPoint, and Access).  
- Programming Languages (R, Python).  

#### **LANGUAGE SKILLS**

- Very good command of English language (Spoken and Written).
- Good command of Spanish language.
- Arabic (Mother tongue).

#### **EXPERIENCE**

#### **2014 till present	Pico International Petroleum	Cairo, EGYPT**
**Lead Geophysicist**  

- Re-evaluated existing prospects and structures, including OIIP calculations and definition of relevant uncertainties and future requirement according to PRMS.   
- Worked with fully integrated team of Drillers, Geoscientists and Reservoir Engineers to define the best well locations and designs for work overs.  
- Seismic stratigraphic and structural interpretation & use of multiple seismic attributes to generate geological model.  
- Applied different techniques of depth conversion to reduce uncertainty and drilling risks.  
- Site survey operation coordinator and operations supervisor, responsible for company cost estimates.    
- 2D and 3D seismic survey designing and planning for onshore Mexico.  
- Prepare G&G lesson learned report after drilling campaign.  
- Presented the technical asset team to the government, third party and certifying body.  
  
#### **2008 till 2014	Pico International Petroleum	Cairo, EGYPT**  

**Geophysicist**

- Created detailed seismic interpretation and review of existing fields, adjacent appraisal targets, undeveloped discoveries and exploration prospects using both 2D and 3D seismic data sets.  
- Well to seismic tie by creating synthetic seismograms, VSP and Correlate time frequency and phase misties. Tailored mistie Analysis for 2D vintages using Kingdom and Petrel packages.  
- Constructed time, depth and attribute maps to provide seismic input to field development and appraisal planning and drilling.  
- Extracted amplitude and Horizon attributes to support defining structural model.  
- Developed velocity analysis, built velocity models and performing Depth conversion Error Analysis.  
- Created 3D static model (Fault model, Horizon model, Property distribution) using petrel Software.  
- Created Fault seal analysis using MS Excel software.  
- Conducted Risk analysis and reserve estimation for onshore Mexico exploration project.  
- Defined fractures trends map upon integrated maps (direct and indirect fractures indicators) to support fracture modeling.  
- Prepared timely technical proposals for drilling undeveloped and exploration prospects according to the agreed drilling sequence.  
- Contributed geophysical input to detailed reservoir geological interpretation, and reserves estimates.  
- Proposed and contribute to the planning and follow up of seismic surveys acquisition, processing and re-processing, if required.  
- Proposed and contribute to the planning and follow up of drilling developing / Exploration wells.  
- Assisted, followed up and monitor the seismic inversion process / technical studies made by a third party.  
- Provided schedules for work, followed up/warning management of any slippage at the earliest possible time and took corrective actions, if required.  
- Witnessed and managed seismic acquisition and processing shallow and deep horizons onshore data.  
- Proposed improvements for working procedures workflow to enhance efficiency and accuracy and to minimize time consuming.  
- Worked as ISO Certificates champion for Exploration department.

#### **EXPERIENCE CONT’D**  

#### **2006 – 2008	EREX Petroleum	Cairo, EGYPT**  

**Seismic Interpreter**  

- Data preparation and loading to Kingdom and Petrel.  
- Synthetic seismograms, Creating and Correlation.  
- Mistie Analysis using Kingdom package.  
- Created Time Maps ,Generated Velocity Analysis and Depth maps.  
- 2D Structural Restoration.  
- Working in Seismic Interpretation for multiple horizons in:  
+ Gulf of Suez Offshore data.  
+ Red Sea in Sudan Offshore data.  
+ Melut basin onshore data.   


#### **Working as instructor for**  

-	Fundmentals of Seismic Interpretation Course.
- Introduction to Machine Learning for Geoscience.
- Machine Learning Application for Geoscientists in Oil and Gas Exploration and Development.
- Introduction to Machine Learning for AlAmal Program 

#### **COMMUNITY ACTIVITIES**  

-	A member of Geophysics Society at Cairo University.  
- Managing the graduation project of final year students in Seismic interpretation, attributes and modeling.  

#### **PERSONAL DATA**  

- Address: 14Hassan Elkady Street, Haram Street,Gizah, Egypt.  
- Tel: +20-11-28920000  
- Email: a_moslim@live.com   
- Date of birth: 1st October 1984.   
- Nationality: Egyptian.  
- Marital Status: Married.
- Military service: Exempted.  


######################################################################

#### **Countries I Have Worked For :**  


```{r}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addMarkers(lng=33.351, lat=28.31, popup="Gulf of Suez Basin") %>%
  addMarkers(lng=33.7, lat=27.5, popup="Southern Gulf of Suez Basin") %>%
  addMarkers(lng=33.53, lat=28.03, popup="Middle Gulf of Suez Basin") %>%
  addMarkers(lng=32.3, lat=29.5, popup="Northern Gulf of Suez Basin") %>%
  addMarkers(lng=29.14, lat=28.4, popup="Western Desert Basin") %>%
  addMarkers(lng=-98.2, lat=22.3, popup="Tampico Misantla Basin") %>%
  addMarkers(lng=-93.2, lat=18.2, popup="South Eastern Basin") %>%
  addMarkers(lng=28.6, lat=31.44, popup="Midetrenean Sea Basin") %>%
  addMarkers(lng=32.29, lat=10.38, popup="Melut Basin") %>%
  addMarkers(lng=37.8, lat=21.4, popup="Red Sea Basin")
  

```

#### **Blocks I Have Participated In Evaluations :**

```{r}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addCircles(lng=33.35, lat=28.3, radius= 100000 ,color = "red" ,popup="Gulf Of Suez Basin") %>%
  addCircles(lng=31.2, lat=36.18, radius= 100000 ,color = "red" ,popup="Jordan") %>%
  addCircles(lng=32.3, lat= 9.7, radius= 100000 ,color = "red" ,popup="Sudan") %>%
  addCircles(lng=-98.2, lat=22.3, radius= 100000 ,color = "red" ,popup="Tampico Misantla Basin") %>%
  addCircles(lng=9.7, lat=33, radius= 100000 ,color = "red" ,popup="Tunis Basin") %>%
  addCircles(lng=-93.2, lat=18.2, radius= 100000 ,color = "red" ,popup="South Eastern Basin") %>%
  addCircles(lng=03.46, lat=56.35, radius= 100000 ,color = "red" ,popup="North Sea Basin") %>%
  addCircles(lng=-98.95, lat=31.17, radius= 100000 ,color = "red" ,popup="Taxes Basin") %>%
  addCircles(lng=28.3, lat=29.8, radius= 100000 ,color = "red" ,popup="Western Desert Basin") %>%
  addCircles(lng=-93.8, lat=18.8, radius= 100000 ,color = "red" ,popup="South Eastern Basin") 

```

##### **References are available upon your request**  