---
title: "My Own Website, Bitecheesssss"
author: "Amrmoslim"
date: "March 30, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

### **PERSONAL PROFILE**


A versatile and highly skilled Geophysicist with 9+ years industry experience, and wide ranging expertise from interpretation in exploration and resource development to 3D depth imaging technology development and application using a wide range of geosciences software. Experienced in seismic interpretation, prospect generation; computer mapping and 3D visualization. Adept at working and communicating across disciplines and management levels. Have been both a popular and highly effective contributor to each of the teams worked with.

### **EDUCATION & TRAINING COURSES**

- B.Sc in Geophysics, Faculty of Science, Cairo University (2006)
-	Project Management MiniMBA, accredited from PMI (Ongoing)
- Structural Restoration Modeling & Fault Prediction 
-	Velocity analysis course, Schlumberger
-	Advanced Seismic Interpretation.
-	Application of Structural Geology in Seismic Data Interpretation.
-	Risk Identification and Assessment.
-	Prospective and Contingent Resources within PRMS. (Gaffney,Cline& Associates)
-	Several QHSE internal awareness sessions.
-	Economics 101 					Stanford online university
-	Reservoir Geomechanics 			Stanford online university	

### **EXTRACURRICULAR ACTIVITIES**

-	Working as freelance instructor for Seismic Interpretation Methods, Fault Seal Analysis and Advanced Seismic Interpretation courses.
- Creating and developing Android application for Fault Seal Analysis Quick look.

### **PROGRAMS & COMPUTER SKILLS**

-	Petrel (Slb)
-	Kingdom (SMT)
-	GeoFrame ( Charisma software- Imain and CPS-3)
-	Lithotect (GLS)  (Restoration)
- Hampson Russell  
???- Office programs (Word, Excel, PowerPoint, and Access).

### **LANGUAGE SKILLS**

- Very good command of English language (Spoken and Written).
- Good command of Spanish language.
- Arabic (Mother tongue).

### **EXPERIENCE**

### **2014 - present	Pico International Petroleum	Cairo, EGYPT**
**Lead Geophysicist**  
-Re-evaluated existing prospects and structures, including OIIP calculations and definition of relevant uncertainties and future requirement according to PRMS.  
-	Worked with fully integrated team of Drillers, Geoscientists and Reservoir Engineers to define the best well locations and designs for work overs.  
???-Seismic stratigraphic and structural interpretation & use of multiple seismic attributes to generate geological model.  
-Applied different techniques of depth conversion to reduce uncertainty and drilling risks.  
-Site survey operation coordinator and operations supervisor, responsible for company cost estimates.  
???-2D and 3D seismic survey designing and planning for onshore Mexico.  
???-Prepare G&G lesson learned report after drilling campaign.  
???-Presented the technical asset team to the government, third party and certifying body.  

### **2008 - 2014	Pico International Petroleum	Cairo, EGYPT**
***Geophysicist** 
???-	Created detailed seismic interpretation and review of existing fields, adjacent appraisal targets, undeveloped discoveries and exploration prospects using both 2D and 3D seismic data sets. 
???-	Well to seismic tie by creating synthetic seismograms, VSP and Correlate time frequency and phase misties. Tailored mistie Analysis for 2D vintages using Kingdom and Petrel packages. 
???-	Constructed time, depth and attribute maps to provide seismic input to field development and appraisal planning and drilling.
???-	Extracted amplitude and Horizon attributes to support defining structural model.
???-	Developed velocity analysis, built velocity models and performing Depth conversion Error Analysis.
???-	Created 3D static model (Fault model, Horizon model, Property distribution) using petrel Software.
???-	Created Fault seal analysis using MS Excel software. 
???-	Conducted Risk analysis and reserve estimation for onshore Mexico exploration project. 
???-	Defined fractures trends map upon integrated maps (direct and indirect fractures indicators) to support fracture modeling.
???-	Prepared timely technical proposals for drilling undeveloped and exploration prospects according to the agreed drilling sequence.
???-	Contributed geophysical input to detailed reservoir geological interpretation, and reserves estimates.
???-	Proposed and contribute to the planning and follow up of seismic surveys acquisition, processing and re-processing, if required.
???-	Proposed and contribute to the planning and follow up of drilling developing / Exploration wells 
???-	Assisted, followed up and monitor the seismic inversion process / technical studies made by a third party.
???-	Provided schedules for work, followed up/warning management of any slippage at the earliest possible time and took corrective actions, if required.
???-	Witnessed and managed seismic acquisition and processing shallow and deep horizons onshore data
???-	Proposed improvements for working procedures workflow to enhance efficiency and accuracy and to minimize time consuming.
- Worked as ISO Certificates champion for Exploration department.

### **EXPERIENCE CONT'D**
### ** 2006 -2008	EREX Petroleum	Cairo, EGYPT**
**Seismic Interpreter** 
???-	Data preparation and loading to Kingdom and Petrel.  
???-	Synthetic seismograms, Creating and Correlation.  
???-	Mistie Analysis using Kingdom package.   
???-	Created Time Maps ,Generated Velocity Analysis and Depth maps   
???-	2D Structural Restoration.  
???-	Working in Seismic Interpretation for multiple horizons in:   
???+ Gulf of Suez Offshore data.  
+	Red Sea in Sudan Offshore data.  
+	Melut basin onshore data.   
### *** COMMUNITY ACTIVITIES**

???-	A member of Geophysics Society at Cairo University  
???-	Managing the graduation project of final year students in Seismic interpretation, attributes and modeling.  
###***PERSONAL DATA**

??? -Address: 14Hassan Elkady Street, Haram Street,Gizah, Egypt.  
-	Tel: +20-11-28920000  
???-	Email: a_moslim@live.com   
???-	Date of birth: 1st October 1984  
???-	Nationality: Egyptian.  
???-	Marital Status: Married.  
???-	Military service: Exempted.  
*** References are available upon your request ***  





######################################################################

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
