---
title: "Oil Price Fetcher"
output:
  html_document: 
    highlight: kate
    theme: united
    toc: yes
date: "April 25, 2019"
---
############################################


###  **Oil Prices Fetcher**

to create Oil Prices Monitors and calculate averages per Years for WTI and Brent 

## The inputs to the model
```{r Links}

# WTI_Daily <- read.csv("https://s3.amazonaws.com/rawstore.datahub.io/718ae3b724d94479a54b3a23bfe8e1fa.csv")
# WTI_Weekly <- read.csv("https://s3.amazonaws.com/rawstore.datahub.io/c63e90f9f9c24a214b6633a1727bb866.csv")
# WTI_Monthly<- read.csv("https://s3.amazonaws.com/rawstore.datahub.io/591144e96162fbca6773c1df30fcd6e1.csv")
WTI_Yearly<- read.csv("https://s3.amazonaws.com/rawstore.datahub.io/07453663141c1232e3552fd58f1d8a8d.csv")

# Brent_Daily <- read.csv("https://s3.amazonaws.com/rawstore.datahub.io/e241a389aa9c167b56a496d05e6153d7.csv" )
# Brent_Weekly <- read.csv( "https://s3.amazonaws.com/rawstore.datahub.io/84a73eef16080a604013e9cd29137dc3.csv")
# Brent_Monthly<- read.csv("https://s3.amazonaws.com/rawstore.datahub.io/7cc48e632633716dc847bb1716854cd3.csv" )
Brent_Yearly<- read.csv( "https://s3.amazonaws.com/rawstore.datahub.io/4b11fe7099f1e3ee6f9a2567f719e092.csv")
 
```

## The expected production per day yearly 
```{r output, echo=TRUE, message=FALSE, warning=FALSE}
knitr::kable(WTI_Yearly, caption = "Table of Yearly Average Price for WTI")

knitr::kable(Brent_Yearly, caption = "Table of Yearly Average Price for Brent")

```

## Graph shows the production forecast for the field life time
```{r Plot}
library(ggplot2)
Brent<-ggplot(Brent_Yearly, aes(Brent_Yearly$Date,Brent_Yearly$Price))+geom_point()+scale_x_date()


plotly:: ggplotly(Brent)
plot(Brent_Yearly,type = "l")
plot(WTI_Yearly,type = "l")

```




```{r cumprod}
 # The Cumulative Production for this Field is about `r Cum.p`  STB based on un interuppted production for a duration of `r Duration`  years and initial Production per day `r df[1,2]`  STB/day and nominal decline rate annually `r DR*100` %. 
```


_**The coming episod, I will show the shiny App that can do this in less than 10 sec with more features.**_ 


############################################
Shinyapp has been created to create production profile without the hassel of changing the code. You can just play with the essential parameters and you get all the results instantaneously.

Please dont hesitate to contact me over a_moslim@live.com to share your comments. 